%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}
\newcommand{\up}[1]{\textsuperscript{#1}}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
            {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}       & #2                 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------

\begin{center}
\textbf{\scshape Yvann LE FAY} \\ \vspace{1pt}
\small 20/01/2000 $|$ +33 6 45 44 70 93 $|$ \href{mailto:yvann.lefay@ensae.fr}{yvann.lefay@ensae.fr} $|$
\href{https://linkedin.com/in/yvann-le-fay/}{linkedin.com/in/yvann-le-fay/} $|$
\href{https://github.com/ylefay}{github.com/ylefay}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
%\resumeSubheading{Paris-Saclay University \& Jyv\"{a}skyl\"{a} University}{Orsay, France \& Jyv\"{a}skyl\"{a}, Finland}{\textbf{P.hD.} in Statistics, jointly supervised by Nicolas Chopin \& Matti Vihola}{2024 - 2027}
%\resumeItemListStart
%\resumeItem{Sequential Monte Carlo methods}
%\resumeItemListEnd
\resumeSubheading
{\'Ecole Normale Supérieure Paris-Saclay - Institut Polytechnique de Paris}{Orsay, France}{\textbf{M.Sc.} in Statistics and Machine Learning, MVA}{2023 - 2024}
\resumeItemListStart
\resumeItem{Optimal transport, learning for time series, probabilistic graphical models, convex optimization, learning \& generation by sampling, bayesian machine learning}
\resumeItemListEnd
\resumeSubheading
{ENSAE Paris - Institut Polytechnique de Paris}{Palaiseau, France}{\textbf{M.Eng.} in Statistics}{2020 - 2024}
\resumeItemListStart
\resumeItem{Sequential Monte Carlo methods, asymptotic and non-asymptotic statistics, econometrics, stochastic calculus}%algorithmic trading
\resumeItemListEnd
\resumeSubheading
{Paris-Saclay University}{Orsay, France}{\textbf{B.Sc.} in Mathematics }
{2020 - 2021}
%\resumeItemListStart
%\resumeItem{General algebra, differential calculus and geometry, complex analysis, ODE and dynamic systems}
%\resumeItemListEnd
\resumeSubheading{Lycée Henri-IV}{Paris, France}
{Program in math, computer science and physics leading to nationwide entrance examinations to the \textit{Grandes Écoles}}{2018 - 2020}
\resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Center for research in Economics and Statistics (CREST)}{Palaiseau, France}
{Research internship, supervised by Nicolas Chopin}{May 2024 - Expected Sep. 2024}
\resumeSubheading
{Aalto University - Simo Särkkä's group}{Espoo, Finland}
{Research internship, supervised by Adrien Corenflos and Pr. Simo Särkkä}{May 2023 - Sep. 2023}
\resumeItemListStart
\resumeItem{Proposed the first probabilistic numerics solver for Stochastic Differential Equations (SDEs) in the additive-noise setting using Gaussian filtering methods. Preprint version: \href{https://arxiv.org/abs/2401.03338}{abs/2401.03338}. Published version: Submitted to Bayesian Analysis. Presented at BAYSM 2023 (ISBA).}
\resumeItem{Companion-code of the article (JAX): \href{https://github.com/ylefay/bayesianSDEsolver}{github.com/ylefay/bayesianSDEsolver}.}
\resumeItemListEnd
\resumeSubheading
{INRIA - MIND}{Palaiseau, France}
{Research internship, supervised by Demian Wassermann}{Jan. 2023 - Mar. 2023}
\resumeItemListStart
\resumeItem{Worked on variational inference methods.}
\resumeItemListEnd
\resumeSubheading
{Lombard Odier Investment Managers' - Multi-Asset}{Geneva, Switzerland}
{Off-cycle internship as a quantitative researcher, supervised by Serge Tabachnik}{Jun. 2022 - Nov. 2022}
\resumeItemListStart
\resumeItem{Contributed to a proprietary scalable and highly modular framework for backtesting cross-asset trading strategies. Researched, implemented and backtested strategies (ARPs, Vol, Momentum). Implemented data mining procedures and modern regression methods. Contributed to a statistics and reporting library. Received a renewal offer.}
\resumeItemListEnd
\resumeSubheading
{Société Générale (CDN, Retail Banking)}{Paris, France}% 8\up{th}}
{Internship in data science and risk analysis, supervised by Pierre Bouché}{Jun. 2021 - Aug. 2021}
\resumeItemListStart
\resumeItem{Backtested a credit decision tool, detected outliers in audit logs. Conducted a study on omnichannel customer behaviours as part of the fusion between Société Générale and Crédit du Nord.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\section{Awards \& Grants}
\resumeSubHeadingListStart
\resumeSubheading{French-Finnish PhD Cotutelle scholarship - the Magnus Ehrnrooth Foundation
}{}{\href{https://www.france.fi/wp-content/uploads/2023/10/Magnus-Ehrnrooth-FI-FR-PhD-Cotutelle.pdf}{france.fi/wp-content/uploads/2023/10/Magnus-Ehrnrooth-FI-FR-PhD-Cotutelle.pdf}}{2024}
\resumeItemListStart
\resumeItem{Received a doctoral grant of 24 000 euros, plus 2 000 euros for travel expenses, per year. The Magnus Ehrnrooth Foundation promotes scientific collaboration between France and Finland by financing international PhD cotutelles.}
\resumeItemListEnd
\resumeSubheading
{Accessit in regional math olympiads}{}{\href{http://euler.ac-versailles.fr/IMG/pdf/olympiades_equipe_2016_palmares.pdf}{euler.ac-versailles.fr/IMG/pdf/olympiades\_equipe\_2016\_palmares.pdf}}{2016}
%\resumeItemListStart
%\resumeItem{Rank 26\up{th}/1640, accessit.}
%\resumeItemListEnd
\resumeSubheading
{Hall of fame - Microsoft Security Response Center}{}{\href{https://msrc.microsoft.com/update-guide/acknowledgement/archive}{msrc.microsoft.com/update-guide/acknowledgement/archive}}{2015}
\resumeItemListStart
\resumeItem{Three times acknowledged for having reported security vulnerabilities.}
\resumeItemListEnd
\resumeSubHeadingListEnd
%-----------PROJECTS-----------
%\section{Projects}
%\resumeSubHeadingListStart
%\resumeSubheading
%{Mirror descent for entropy-regularized optimal transport}{2024}{\href{https://github.com/ylefay/greenkhorn_apdamd/}{github.com/ylefay/greenkhorn\_apdamd}}{Python, JAX.}
%\resumeSubheading
%{High dimensional Vector Autoregression (VAR) model estimation via Tensor decomposition}{2023}{\href{https://github.com/ylefay/high_dimensional_vector_autoregression}{github.com/ylefay/high\_dimensional\_vector\_autoregression}}{Python, JAX.}
%\resumeSubheading
%{Linear and Non-linear Independent Component Analysis}{2023}{\href{https://github.com/ylefay/independent_component_analyisis}{github.com/ylefay/independent\_component\_analysis}}{Python, JAX.}
%\resumeSubheading
%{Bayesian SDE samplers}{2023}{\href{https://github.com/ylefay/bayesianSDEsolver}{github.com/ylefay/bayesianSDEsolver}}{Python, JAX.}
%\resumeSubHeadingListEnd
%-----------PROGRAMMING SKILLS-----------
\section{Programming Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages}{: Python, Ocaml, Wolfram Language, SQL} \\
\textbf{Technical stack}{: Git, Linux, Bloomberg, Excel}\\
\textbf{Libraries and others}{: JAX, PySpark, Dask, blp}

}}
\end{itemize}
%-----------------------------------------
\section{Others}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages}{: French, English} \\
\textbf{Citizenships}{: French, Swiss}\\
}}
\end{itemize}
%-------------------------------------------
\end{document}

